Capstone Movielens Report

### 2025-10-20 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the following functions: get_log1, print_log1, put_log1.

This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.

@@

The source code of the [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) function is shown below:
```{r eval=FALSE}
print_log1 <- function(msg_template, arg1){
  print(get_log1(msg_template, arg1))
}
```

@@

Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1).

@@

::: { #func.put_log1.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log1.args.msg_template) argument.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
:::

@@

The source code of the [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) function is shown below:
```{r eval=FALSE}
put_log1 <- function(msg_template, arg1){
  put(get_log1(msg_template, arg1))
}
```

>>>>

This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [print_log1](#func.print_log1) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [print_log1](#func.print_log1) function described above.

@@

The source code of the [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) function is shown below:
```{r eval=FALSE}
print_log1 <- function(msg_template, arg1){
  print(print_log1(msg_template, arg1))
}
```

@@

Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log1.args.msg_template) argument using the format value specified by the [arg1](#func.put_log1.args.arg1).

@@

::: { #func.put_log1.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log1.args.msg_template) argument.

@@

This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [put_log1](#func.put_log1) function described above.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [put_log1](#func.put_log1) function described above.
:::

@@

The source code of the [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) function is shown below:
```{r eval=FALSE}
put_log1 <- function(msg_template, arg1){
  put(put_log1(msg_template, arg1))
}
```
